---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rosenkohl

<!-- badges: start -->
<!-- badges: end -->

The goal of rosenkohl is to easily load some frequently used helper functions.
They are mostly useful for on-the-fly testing and or preparations.

## Installation

You can install the development version of rosenkohl from [GitHub](https://github.com/brueckmann/rosenkohl) with:

``` r
# install.packages("pak")
pak::pak("brueckmann/rosenkohl")
```

## Example

This is a basic example which shows you how to sort a string alphabetically, using `abc()`. This is intended to be used *interactively*, therefore, it comes with multiple output formats.

```{r example abc}
library(rosenkohl)
## basic example code

### assume you have unordered strings
x <- "charlie, delta, alpha,bravo"
y <- c("delta", "charlie bravo", "alpha")

### see the different output formats and the aliases
abc(x, format_output = TRUE)
alphabetise(x, format_output = FALSE)
abc(x, format_output = "inline")

abc(y, format_output = TRUE)
abc(y, format_output = FALSE)
alphabetize(y, format_output = "inline")

```

This is a (very constructed) example which shows how `sourcelines()` works.
```{r example sourcelines}
library(rosenkohl)
## basic example code

# create a file to source it 
inputfile <-  tempfile(fileext = ".R")
# Write content to the file
writeLines(text = "1+0 \n 2+0 \n 3+0",
           con = inputfile)
# Check the file exists
file.exists(inputfile)
# source whole file loudly
source(inputfile, echo = TRUE)

# source first line
sourcelines(inputfile, 1, TRUE)
# source second and third line
sourcelines(inputfile, 2:3, TRUE)
# source first and third till (non-existing fourth) line
sourcelines(inputfile, c(1,3:4), TRUE)

```


This is a tiny example of how `add_date()` can be used:
```{r example add date}
library(rosenkohl)
## basic example code
add_date("example", "_from_")
add_date("today.R")

# create temp folder with subfolder demo
# define your path
temp <- file.path(tempdir(), "demo")
# remove everything in temp
unlink(temp, recursive = TRUE)   
# create directory 
dir.create(temp)

writeLines("x",        
           file.path(temp, 
                     add_date("test.R")
           )
) 

#return file names 
list.files(temp)

```




## Bug reports

Report an issue on [https://github.com/brueckmann/rosenkohl/issues](https://github.com/brueckmann/rosenkohl/issues).

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. -->

