---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rosenkohl

<!-- badges: start -->
[![R-CMD-check](https://github.com/brueckmann/rosenkohl/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/brueckmann/rosenkohl/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of rosenkohl is to easily load some frequently used helper functions.
They are mostly useful for on-the-fly testing and or data preparations. 

**NOTE:** This is mostly a toy package created because of a discussion over lunch at [Uni Bern's IPW](https://www.ipw.unibe.ch/). My colleagues thought I was (still) talking about [R Packages](https://r-pkgs.org), when I mentioned [rosenkohl](https://upload.wikimedia.org/wikipedia/commons/d/d4/Brussels_sprouts_-_geograph.org.uk_-_684256.jpg?utm_source=commons.wikimedia.org&utm_campaign=index&utm_content=original), Brussels sprouts. Somehow, we ended up joking that this R package should exist. Now, it does! I use it to bundle helper functions I sometimes use.

## Installation

You can install the development version of rosenkohl from [GitHub](https://github.com/brueckmann/rosenkohl) with:

``` r
# install.packages("pak")
pak::pak("brueckmann/rosenkohl")
```

## Examples

### ABC function

This is a basic example which shows you how to sort a string alphabetically, using `abc()`. This is intended to be used *interactively*, therefore, it comes with multiple output formats.

```{r example abc}
library(rosenkohl)
## basic example code

### assume you have unordered strings
x <- "charlie, delta, alpha,bravo"
y <- c("delta", "charlie bravo", "alpha")

### see the different output formats and the aliases
abc(x, format_output = TRUE)
alphabetise(x, format_output = FALSE) # use the alias
abc(x, format_output = "inline")

abc(y, format_output = TRUE)
abc(y, format_output = FALSE)
alphabetize(y, format_output = "inline") # use the alias

```

### add_date function
This is a tiny example of how `add_date()` can be used:
```{r example add date}
library(rosenkohl)
## basic example code
add_date("example", "_from_")
add_date("today.R")

# create temp folder with subfolder demo
# define your path
temp <- file.path(tempdir(), "demo")
# remove everything in temp
unlink(temp, recursive = TRUE)   
# create directory 
dir.create(temp)

writeLines("x",        
           file.path(temp, 
                     add_date("test.R")
           )
) 

#return file names 
list.files(temp)

```


### cleanup function

This exemplifies the cleanup function `cleanup()`.
The function can also be called by their aliases `tempex()` or `temprm()`.

```{r example cleanup}
library(rosenkohl)

## Create some noise. 
### create things to be kept
temptation_to_keep <- data.frame(x = 1, 
                         y = 1:10, 
                         char = sample(LETTERS[1:3], 10, replace = TRUE))
url_to_keep <- "https://www.nothing_temp.csv"
### create things to be deleted: 
list_temp <- c(char = sample(LETTERS[1:3], 10, replace = TRUE))
temp_url <- "https://raw.githubusercontent.com/tidyverse/dplyr/main/data-raw/starwars.csv"
temp_dir <- file.path(tempdir(), "demo")
#### define a temp function
temp_function <- function(x) {
x + 1
}
## Some noice was created.
# use function but turn off  verbose
cleanup(verbose = FALSE)

# use function with own pattern
cleanup(pattern = "_to_keep")

## create another temporary list again
temporary_list <- c("something", "else")
# use function with own pattern
cleanup(pattern="temporary_")

# use function when nothing is available that matches the pattern
cleanup(pattern="precious")

# use function when nothing is available matching the pattern - but a function
cleanup()

# remove the temp-function
cleanup(keep.functions = FALSE)

```

### lazysave function
This is a tiny example of how to save with `lazysave()`:
```{r example lazysave}
library(rosenkohl)

# create a dataframe called data
data <- data.frame(x = 1, 
                   y = 1:10, 
                   char = sample(LETTERS[1:3], 10, replace = TRUE))

# create temp folder with a subfolder
# define your path
temp <- file.path(tempdir(), "demo")
# remove everything in temp
unlink(temp, recursive = TRUE)   
# create directory 
dir.create(temp)


lazysave(data)
list.files(temp) # still empty, as default path out is tempdir.

# you may append the date to the filename
lazysave(data, dir = temp, date=TRUE, datesep = "", extension = "rdata")
# return file names 
list.files(temp) # file saved.

# lazysave() doesn't mind dot(s) in extensions  (but rds is the default)
lazysave(data, dir = temp, date=TRUE, datesep = "-", extension = ".r.ds.")
# lazysave() doesn't mind capitalisation or not in extension
lazysave(data, dir = temp, extension = "RDATA")

```



### sourcelines function

This is a (very constructed) example which shows how `sourcelines()` works.
```{r example sourcelines}
library(rosenkohl)
## basic example code

# create a file to source it 
inputfile <-  tempfile(fileext = ".R")
# Write content to the file
writeLines(text = "1+0 \n 2+0 \n 3+0",
           con = inputfile)
# Check the file exists
file.exists(inputfile)
# source whole file loudly
source(inputfile, echo = TRUE)

# source first line
sourcelines(inputfile, 1, TRUE)
# source second and third line
sourcelines(inputfile, 2:3, TRUE)
# source first and third till (non-existing fourth) line
sourcelines(inputfile, c(1,3:4), TRUE)

```


### summ_unique function

This is a (very constructed) example which shows how `summ_unique()` works.
```{r example summarise unique}
library(rosenkohl)
## basic example code

# generate an example dataframe
df_no_na <- data.frame(x = 1, # 1 unique value
y = 1:10, # 10 unique values 
char = sample(LETTERS[1:3], 10, replace = TRUE)) # max 3 unique values
summ_unique(df_no_na) 
# add row with NAs
row <- c(NA, 10, NA)
df_with_NAs <- rbind.data.frame(df_no_na, row)
summarise_unique(df_with_NAs) # use the alias
summ_unique(df_with_NAs, has.na = TRUE)  # show if cols have NAs

# See what happens when everything is NA
num_na <- row[-2] # numeric NA
logi_na <- c(NA, NA) # logical NA
char_na <- c(NA_character_,NA_character_) # character NA
df_na <- data.frame(num_na, logi_na, char_na)
summ_unique(df_na)

```


## Bug reports

Report an issue on [https://github.com/brueckmann/rosenkohl/issues](https://github.com/brueckmann/rosenkohl/issues).

## Even 

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. -->

